---
title: "SpectralPermutationRecovery"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SpectralPermutationRecovery}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#library(SpectralPermutationRecovery)
```

## Introduction

Generally speaking, the spectral permutation recovery method takes a data matrix
`data`
with disordered columns as input, and outputs a vector giving a natural order of the columns. In the first step, each row is centered to have mean zero,

```r
data.c <- data - (rowMeans(data) %o% rep(1, dim(data)[2]))
```

In the second step, we apply SVD to the row-centered matrix and extract the first right singular vector,

```r
v1 <- svd(data.c)$v[,1]
```

associated with the largest singular value. The order of columns are inferred based on the relative magnitude of the `v1` component.

## Installation



## Usage

Common usage examples
